---
title: "sims"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file tries to simulate data that varies number of trials and the number of
participants to try to get a sense of what smaller N but higher trials per 
participant might look like formally. 

The motivation for doing so follows from reading these three papers:

1) Power contours: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8329985/

2) Small is Beautiful: https://doi.org/10.3758/s13423-018-1451-8

3) Event history analysis: https://doi.org/10.1177/2041669520978673

The first two for obvious reasons, as they show that "power" emerges from sample 
size and trial count. And depending on the structure of the data, one or the other
can be more influential in determining power.

The third paper because when we interviewed Sven, he used EHA, and I wasn't sure
how power or precision would be estimated in those types of analyses. This is 
because you have block (if time is binned) by other factors. So the analysis could
be rather complex in terms of design etc. e.g., 14 bins by however many other 
factors.

So, the aim here is to become more familiar estimating power/precision as a function 
of sample size and trial count in the types of designs that we might typically use.


## load the libraries that we will be using ## 

## install ##

```{r install-pkg}
# install.packages("remotes")
# remotes::install_github("stan-dev/cmdstanr")
# 
# install.packages("devtools")
# devtools::install_github("jmgirard/standist")
# 
# install.packages(c("tidyverse", "RColorBrewer", "patchwork", "brms",
#                    "tidybayes", "bayesplot", "patchwork", "future", "faux"))
```

take a snapshot of loaded packages and update the lock.file using renv

```{r snapshot-renv}
# take a snapshot and update the lock.file
# renv::snapshot() # this is only necessary when new packages or installed or packages are updated.
```

## load ##

```{r load-pkg}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "faux")

lapply(pkg, library, character.only = TRUE)
```

## settings ##

```{r set-options}
options(brms.backend = "cmdstanr",
        mc.cores = parallel::detectCores(),
        future.fork.enable = TRUE,
        future.rng.onMisuse = "ignore") ## automatically set in RStudio

supportsMulticore()

detectCores()
```


## simulate some data ##

- describe the example design/s, which vary in complexity. dv=rt. This is a 
src design, with parameters determined by past research. So they should be in a 
reasonable ballpark estimate for speeded RT tasks with two options. That also
includes estimates of SD, cors between conditions etc.

d - congr vs incon, varying intercepts and slopes for pid and items.

Also make a note about the choice of distribution. e.g., RT data tends to be 
left skewed and gaussian models are a sub-optimal fit. Various other dists are better
e.g., link here: https://lindeloev.shinyapps.io/shiny-rt/. Shifted lognormal, 
for example, is one that we have used before in our own work. For simplicity and 
convenience, we will generate gaussian data here and use a gaussian model. 


simulate some data in original units (RT)

```{r}
# make it reproducible
set.seed(1)

# define parameters
subj_n = 25  # number of subjects
item_n = 10  # number of items (10 faces x 8 repeats (half gaze left))
rep_n = 8 # number of trial repeats per item e.g., face1 is shown X times per pid 50% L, 50% C
b0 = 725      # intercept
b1 = 50      # fixed effect of condition
u0s_sd = 50   # random intercept SD for subjects
u1s_sd = 10   # random b1 slope SD for subjects
u0i_sd = 25   # random intercept SD for items 
u1i_sd = 5   # random b1 slope SD for items
r01s = 0.3   # correlation between random effects 0 and 1 for subjects
r01i = 0.3   # correlation between random effects 0 and 1 for items
sigma_sd = 50 # error SD

# set up data structure
dat <- add_random(subj = subj_n, item = item_n, rep = rep_n) %>%
  # add and recode categorical variables
  add_within("item", gaze = c("left", "right")) %>%
  add_within("subj", condition = c("congr", "incong")) %>%
  add_contrast("condition", "anova", add_cols = TRUE, colnames = "cond") %>%
  # add random effects 
  add_ranef("subj", u0s = u0s_sd, u1s = u1s_sd, .cors = r01s) %>%
  add_ranef("item", u0i = u0i_sd, u1i = u1i_sd, .cors = r01i) %>%
  add_ranef(sigma = sigma_sd) %>%
  # calculate DV
  mutate(rt = b0 + u0s + u0i + (b1 + u1s + u1i) * cond + sigma)

head(dat)
str(dat)
summary(dat)

# save initial data
# write_csv(dat, "data/dat.csv")
```

density plot

```{r}
ggplot(dat, aes(x=rt, fill=condition)) +
   geom_density(alpha = 0.3, colour = "darkgrey") +
   scale_fill_brewer(palette = "Dark2")+
   theme_bw()+
   theme(panel.grid = element_blank()) +
   theme(legend.position = "none") +
   ggtitle("rt by condition")
# ggsave ("figures/density.jpeg")
```


and now in standardised units (this is not meant to be identical to the 
original unit data, but it does have the same structure, but the effect sizes
are different. That's because I just guessed an RT difference above of 50ms
and I used 0.5 d below, so they do not correspond. But they don't need to.)

```{r}
# make it reproducible
set.seed(1)

# define parameters
subj_n = 25  # number of subjects
item_n = 10  # number of items (4 faces x 2 repeats (half gaze left))
rep_n = 8 # number of trial repeats per item e.g., face1 is shown X times per pid 50% L, 50% C
b0 = 0      # intercept
b1 = 0.5      # fixed effect of condition
u0s_sd = 0.5   # random intercept SD for subjects
u1s_sd = 0.1   # random b1 slope SD for subjects
u0i_sd = 0.05   # random intercept SD for items
u1i_sd = 0.01   # random b1 slope SD for items
r01s = 0.1   # correlation between random effects 0 and 1 for subjects
r01i = 0.1   # correlation between random effects 0 and 1 for items
sigma_sd = 1 # error SD

# set up data structure
dats <- add_random(subj = subj_n, item = item_n, trep = rep_n) %>%
  # add and recode categorical variables
  add_within("item", gaze = c("left", "right")) %>%
  add_within("subj", condition = c("congr", "incong")) %>%
  add_contrast("condition", "anova", add_cols = TRUE, colnames = "cond") %>%
  # add random effects
  add_ranef("subj", u0s = u0s_sd, u1s = u1s_sd, .cors = r01s) %>%
  add_ranef("item", u0i = u0i_sd, u1i = u1i_sd, .cors = r01i) %>%
  add_ranef(sigma = sigma_sd) %>%
  # calculate DV
  mutate(rt = b0 + u0s + u0i + (b1 + u1s + u1i) * cond + sigma)

head(dats)
str(dats)
summary(dats)
```

density plot

```{r}
ggplot(dats, aes(x=rt, fill=condition)) +
   geom_density(alpha = 0.3, colour = "darkgrey") +
   scale_fill_brewer(palette = "Dark2")+
   theme_bw()+
   theme(panel.grid = element_blank()) +
   theme(legend.position = "bottom") +
   ggtitle("rt by condition")
# ggsave ("figures/density.jpeg")
```


## Can we calculate relevant values for a power contour sim?? ##

see Baker et al., page 298 for the RT example.

let's first do the original unit data

this is what we need at the end

```{r}
N <- 25 # sample size
k <- 160 # trial count (per condition??)
diff <- 48.7 # difference score in original units
sd_s <- 71.6 # sd of the diff
sd_w <- 103 # sd within
sd_b <- 71.1 # sd between
sd_ratio <- sd_w / sd_b
d <- diff / sd_s
```

This means we need to calculate the difference score and the sd of the diff

here we get diff (as mean_diff), sd_s and d

```{r}
d_diff <- dat %>% 
  pivot_wider(id_cols = c(subj, item, rep, gaze),
              names_from = "condition",
              values_from = "rt") %>% 
  mutate(diff = incong - congr,
         mean_diff = mean(diff),
         sd_s = sd(diff),
         d = mean_diff/sd_s) 
d_diff

# assign these values in the chunk above
# diff = 48.7
# sd_s = 71.6
```

now sigma_w

```{r}
sigma_w <- d_diff %>% 
  summarise(sd_c = sd(congr),
            sd_i = sd(incong),
            all_within = sqrt(sd(congr)^2 + sd(incong)^2))
sigma_w

# assign these values in the chunk above
# sd_w = 103
```

now sigma_b 

```{r}
sigma_b <- sqrt(sd_s^2 - ((sd_w^2)/k))
sigma_b

# assign these values in the chunk above
# sd_b = 71.1
```


and now standardised units



```{r}
N <- 25 # sample size
k <- 160 # trial count (per condition??)
diff <- 0.53 # difference score in original units
sd_s <- 1.43 # sd of the diff
sd_w <- 1.58 # sd within
sd_b <- 1.42 # sd between
sd_ratio <- sd_w / sd_b
d <- diff / sd_s
```

This means we need to calculate the difference score and the sd of the diff

here we get diff (as mean_diff), sd_s and d

```{r}
ds_diff <- dats %>% 
  pivot_wider(id_cols = c(subj, item, trep, gaze),
              names_from = "condition",
              values_from = "rt") %>% 
  mutate(diff = incong - congr,
         mean_diff = mean(diff),
         sd_s = sd(diff),
         d = mean_diff/sd_s) 
ds_diff

# assign these values in the chunk above
# diff = 0.528
# sd_s = 1.43
# d = 0.37
```

now sigma_w

```{r}
sigma_ws <- ds_diff %>% 
  summarise(sd_c = sd(congr),
            sd_i = sd(incong),
            all_within = sqrt(sd(congr)^2 + sd(incong)^2))
sigma_ws

# assign these values in the chunk above
# sd_w = 1.58
```

now sigma_b 

```{r}
sigma_bs <- sqrt(sd_s^2 - ((sd_w^2)/k))
sigma_bs

# assign these values in the chunk above
# sd_b = 1.42
```


## Plug in the values to the power contours app ##

Go here and plug in values: https://shiny.york.ac.uk/powercontours/

That will determine the balance between N and trials required for a range of 
different levels of power.


## Queries ##

Using the above values doesn't quite seem right to me based on the output from 
the power contours shiny app. Or at least the number of trials vs pts seems too 
low, given this type of data?? e.g., N=22, K=10 for the original units dataset.

Having said that, if you plug in the values from Sim 1 of their Power contours 
paper, you get N = 17, K = 7 for 80% power. So that is in the same ballpark for 
a very similar RT compatibility dataset.


Maybe aim for 90 or 95% power?

And set alpha at 0.005?

For the original units data, this translates to N=50, K=10 for 90% power.

## Questions ##


ok, at this point, a bunch of questions crop up.


What is the relationship between varying intercepts / effects in a multi-level 
model and within vs between SD?

How can we simulate data which varies within vs between? Is there any need if 
the power contours paper has things setup to do just that?

Is K trials per condition or total trials? I think per condition.


How can we simulate data to think about precision rather than power? Or at least
precision as well as power? I guess we could take the same simulation approach
as we have used in other sims and generate 1000 datasets and vary the trial count
and the sample size? e.g., 

N=10, 20, 50.
K=10, 20, 50.

and then calculate widths of the intervals generated.


Is there any need to do the modelling approach across pts, if Smith and Little 
are arguing that it should be done in single pts with other pts being the 
natual "replicate"? What would that kind of analysis look like? Bayesian model
with N=1? Not sure. There are other methods of course, see Phillipe Shyns work
and Sam Schwarzkopf's work. 

## workflow conclusions ##

The current approach above follows these principles:

1. generate multi-level data either via educated simulations or by past data giving
good estimates of SDs, cors and effect sizes etc.

2. Calculate within vs between SD.

3. Plug in the relevant values into the power contours shiny and get a sense for
the balance between trials and participants.

This approach gives you a good idea or intuition maybe about N and K. But it 
still feels somehow unsatisfying. Or maybe I just prefer the 
simulation approach. Or maybe use the values from step (3) to generate a sense, 
then use the sim approach afterwards to refine the specifics and calculate precision.??

So, a possible step 4 could be:

4. Simulate data and estimate models that vary N and K, in order to estimate 
precision across such designs. 



## simulate data and vary N and K ##

just a quick test

## create a function to simulate multiple datasets ##

```{r}
sim <- function(subj_n = 25, item_n = 10, rep_n = 8,  # these can be changed when calling the function
                b0 = 0, b1 = 0.5,         # fixed effects 
                u0s_sd = 0.5, u0i_sd = 0.05,   # random intercepts subj and item
                u1s_sd = 0.1, u1i_sd = 0.01,   # random slope subj and item
                r01s = 0.1, r01i = 0.1,   # cor
                sigma_sd = 1,           # error term
                ... # helps the function work with pmap() below
                ) {

  # set up data structure
  data <- add_random(subj = subj_n, item = item_n, trep = rep_n) %>%
  # add and recode categorical variables
  add_within("item", gaze = c("left", "right")) %>%
  add_within("subj", condition = c("congr", "incong")) %>%
  add_contrast("condition", "anova", add_cols = TRUE, colnames = "cond") %>%
  # add random effects
  add_ranef("subj", u0s = u0s_sd, u1s = u1s_sd, .cors = r01s) %>%
  add_ranef("item", u0i = u0i_sd, u1i = u1i_sd, .cors = r01i) %>%
  add_ranef(sigma = sigma_sd) %>%
  # calculate DV
  mutate(rt = b0 + u0s + u0i + (b1 + u1s + u1i) * cond + sigma)
  
  # glimpse(data) # only use this when testing the code
}

```

Here’s a quick example of how our function works. You can change these parameters
and create some different data.

```{r}
sim(subj_n = 25, item_n = 10, rep_n = 2, b0 = 0, b1 = 0.5) # if you uncomment glimpse above,
# it will let you glimpse the data that's generated. this is useful for checking / testing code purposes.
```

## run the simulations and iterate through exps and variables ##

Here we just run 100 replicates because this is a demo. For the real thing, 
something more like 1000 replicates would be more appropriate.

## run sims and keep the data and model objects in the output ##

this version keeps all the data and models (but sucks up memory), so it is mainly
good for testing the code and checking the output rather than the real thing.

Here, for example, I use it to test the code with 2 exp sims.

To start with just simulate data and don't build models. Just get a sense of 
the descriptive statistics.

```{r}
plan(multicore)
x <- crossing(
  exp = 1:100, # number of experiment replicates
  subj_n = c(10, 20, 50), # range of subject N
  rep_n = c(2, 5, 10, 100)
) %>%
  mutate(d = pmap(., sim)) # %>%
  #mutate(fit = map2(d, exp, ~update(fit, newdata = .x, seed = .y)))
```

let's take a look

```{r}
head(x)
tail(x)
```

unnest to expand the data.

```{r}
sim_dat <-
  x %>% 
  unnest(d)
head(sim_dat)

write_csv(sim_dat, "data/sim_dat_2.csv")
```

## plot ##

code factors (for plotting)

```{r}
## read in if necessary
# sim_dat <- read_csv("data/sim_dat.csv")
# sim_dat <- read_csv("data/sim_dat_2.csv")

sim_dat <- 
  sim_dat %>% 
  mutate(exp = factor(exp),
         subj_n = factor(subj_n),
         rep_n = factor(rep_n),
         condition = factor(condition, 
                            levels = c("congr", "incong")))
head(sim_dat)
```

and plot

data 

```{r}
ggplot(sim_dat, aes(x=rt, fill=condition)) +
   geom_density(alpha = 0.5, colour = "darkgrey") +
   scale_fill_brewer(palette = "Dark2")+
   theme_bw()+
   theme(panel.grid = element_blank()) +
   theme(legend.position = "bottom") +
   ggtitle("rt by condition, rep_n and N") +
   facet_grid(fct_rev(subj_n)~rep_n)

ggsave ("figures/rt_density.jpeg",
        width = 6, height = 6)
```

calculate a difference score

```{r}
sim_diff <- sim_dat %>% 
  pivot_wider(id_cols = c(exp, subj_n, rep_n, subj, item, trep, gaze),
              names_from = "condition",
              values_from = "rt") %>% 
  mutate(diff = incong - congr)
head(sim_diff)
```

create summary data

at the pid level 

(this would be useful for treating individual pids as replicates or for plotting
data by pid)

```{r}
summary_diff_pid <- sim_diff %>%
  group_by(exp, subj_n, rep_n, subj) %>%
  summarise(mean_diff = mean(diff),
            sd = sd(diff),
            n = n(), # n here is the total number of trials (cong & incong)
            sem = (sd/sqrt(n())),
            ci = sem*1.96)
head(summary_diff_pid)
tail(summary_diff_pid)
```

at the group level

```{r}
summary_diff <- sim_diff %>% 
  group_by(exp, subj_n, rep_n) %>% 
  summarise(mean_diff = mean(diff),
            sd = sd(diff),
            n = length(unique(subj)), # n here is the total subjs
            sem = (sd/sqrt(length(unique(subj)))),
            ci = sem*1.96)
head(summary_diff)
```

quick plot with pid data

plot settings

```{r}
## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

violin

```{r}
ggplot(summary_diff_pid, 
               aes(x = rep_n, y = mean_diff, fill = rep_n)) +
  geom_jitter(width = 0.1, alpha = 1, colour = "darkgrey") +
  geom_violin(alpha = 0.7, position=pd2) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw() +
  facet_wrap(~subj_n) 
```

this looks sensible by trial count but is sample N right? It doesn't seem to 
change very much as sample size increases...whereas the histogram below looks
like it changes by both...

at the group level

density

```{r}
p_dens <- ggplot(summary_diff, aes(x=mean_diff, fill=rep_n)) +
   geom_density(alpha = 0.7, colour = "darkgrey") +
   scale_fill_brewer(palette = "Dark2")+
   theme_bw()+
   # theme(panel.grid = element_blank()) +
   theme(legend.position = "none") +
   ggtitle("difference score by condition, rep_n and N") +
   facet_grid(fct_rev(subj_n)~rep_n)
p_dens

ggsave ("figures/diff_dens.jpeg",
        width = 6, height = 6)
```

histogram

```{r}
ggplot(summary_diff, aes(x=mean_diff, fill=rep_n, colour = rep_n)) +
   geom_histogram(binwidth = .01, position = 'identity', alpha = 0.5) +
   geom_rug(linewidth = 1/6) +
   scale_fill_brewer(palette = "Dark2",
                     breaks=c('1', '2', '5', '10'),
                     labels=c("10", "20", "50", "100")) +
   scale_colour_brewer(palette = "Dark2",
                       breaks="none") +
   theme_bw() +
   theme(legend.position = "bottom") + 
   # scale_x_continuous(breaks = seq(0.4, 1.1, 0.1)) +
   ggtitle("difference score by rep_n and N") +
   facet_wrap(~subj_n)

# switch the arrangement between subj_n and rep_n
ggplot(summary_diff, aes(x=mean_diff, fill = subj_n, colour = subj_n)) +
   geom_histogram(binwidth = .01, position = 'identity', alpha = 0.5) +
   geom_rug(linewidth = 1/6) +
   scale_fill_brewer(palette = "Dark2",
                     breaks=c('10', '20', '50')) +
   scale_colour_brewer(palette = "Dark2",
                       breaks="none") +
   theme_bw() +
   theme(legend.position = "bottom") + 
   # scale_x_continuous(breaks = seq(0.4, 1.1, 0.1)) +
   ggtitle("difference score by rep_n and N") +
   facet_wrap(~rep_n, ncol = 1)

# facet_grid
p_hist <- ggplot(summary_diff, aes(x=mean_diff, fill=rep_n, colour = rep_n)) +
   geom_histogram(binwidth = .01, alpha = 0.7) +
   geom_rug(linewidth = 1/6) +
   scale_fill_brewer(palette = "Dark2",
                     breaks=c('1', '2', '5', '10'),
                     labels=c("10", "20", "50", "100")) +
   scale_colour_brewer(palette = "Dark2",
                       breaks="none") +
   theme_bw() +
   theme(legend.position = "none") + 
   # scale_x_continuous(breaks = seq(0.4, 1.1, 0.1)) +
   ggtitle("difference score by rep_n and N") +
   facet_grid(fct_rev(subj_n)~rep_n)
p_hist

ggsave ("figures/diff_hist.jpeg",
        width = 6, height = 6)
```


## calculate widths ##

widths = ci*2 in this case?? That is, the full width (or both arms).

```{r}
summary_diff <- summary_diff %>% 
  mutate(width = ci*2)
summary_diff
```

plot widths

```{r}
## separate panels
p_width <- ggplot(summary_diff, aes(x=width, fill=rep_n, colour = rep_n)) +
   geom_histogram(binwidth = .01, alpha = 0.7) +
   geom_rug(linewidth = 1/6) +
   scale_fill_brewer(palette = "Dark2",
                     breaks=c('1', '2', '5', '10'),
                     labels=c("10", "20", "50", "100")) +
   scale_colour_brewer(palette = "Dark2",
                       breaks="none") +
   theme_bw() +
   theme(legend.position = "none") + 
   # scale_x_continuous(breaks = seq(0.4, 1.1, 0.1)) +
   ggtitle("difference score by rep_n and N") +
   facet_grid(fct_rev(subj_n)~rep_n)
p_width

# ggsave ("figures/width_hist.jpeg",
#         width = 6, height = 6)

p_width <- ggplot(summary_diff, aes(x=width, fill=subj_n, colour = subj_n)) +
   geom_histogram(binwidth = .01, alpha = 0.7) +
   geom_rug(linewidth = 1/6) +
   scale_fill_brewer(palette = "Dark2",
                     breaks=c('50', '20', '10')) +
   scale_colour_brewer(palette = "Dark2",
                       breaks="none") +
   theme_bw() +
   theme(legend.position = "bottom") + 
   scale_x_continuous(breaks = seq(0.7, 2, 0.1)) +
   ggtitle("95% CI width by rep_n and N") +
   facet_wrap(~rep_n, ncol = 1)
p_width

ggsave ("figures/width_hist.jpeg",
        width = 6, height = 8)
```

calculate avg width

```{r}
summary_diff %>%
  group_by(subj_n, rep_n) %>%
  summarise(avg_width = mean(width))

#   subj_n rep_n avg_width
#    <fct>  <fct>     <dbl>
#  1 10     1         1.76 
#  2 10     2         1.76 
#  3 10     5         1.76 
#  4 10     10        1.76 
#  5 20     1         1.26 
#  6 20     2         1.24 
#  7 20     5         1.24 
#  8 20     10        1.24 
#  9 50     1         0.783
# 10 50     2         0.784
# 11 50     5         0.787
# 12 50     10        0.786
```

what about % under a width reference (reference values were simply taken from the
means above as an approximate guide)

```{r}
summary_diff %>%
  group_by(subj_n, rep_n) %>% 
  mutate(below_1.8 = if_else(width < 1.8, 1, 0),
         below_1.3 = if_else(width < 1.3, 1, 0),
         below_0.8 = if_else(width < .8, 1, 0)) %>% 
  summarise(power_1.8 = mean(below_1.8),
            power_1.3 = mean(below_1.3),
            power_0.8 = mean(below_0.8))

#   subj_n rep_n power_1.8 power_1.3 power_0.8
#    <fct>  <fct>     <dbl>     <dbl>     <dbl>
#  1 10     1          0.67      0         0   
#  2 10     2          0.75      0         0   
#  3 10     5          0.82      0         0   
#  4 10     10         0.93      0         0   
#  5 20     1          1         0.81      0   
#  6 20     2          1         0.99      0   
#  7 20     5          1         0.99      0   
#  8 20     10         1         1         0   
#  9 50     1          1         1         0.83
# 10 50     2          1         1         0.89
# 11 50     5          1         1         0.95
# 12 50     10         1         1         1   
```


## calculate and plot power ##

calculate power i.e., % Q2.5 > 0

```{r}
power <- summary_diff %>% 
  group_by(subj_n, rep_n) %>%
  mutate(Q2.5 = mean_diff - ci,
         check = ifelse(Q2.5 > 0, 1, 0)) %>% 
  summarise(power = mean(check))
power
```

plot power

```{r}
p_power <- ggplot(power, aes(rep_n, subj_n, fill = power)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f", power)), color = "white", size = 10) +
  scale_fill_viridis_c(limits = c(0, 1))
p_power

ggsave ("figures/power.jpeg",
        width = 6, height = 6)
```

## plot difference scores and include power as a text label ##

wrangle

```{r}
plot_diffs <- summary_diff %>%
  mutate(Q2.5 = mean_diff - ci,
         Q97.5 = mean_diff + ci,
         below_zero = if_else(Q2.5 < 0, "yes", "no"), 
         below_zero = factor(below_zero, levels = c("no", "yes"))) %>% 
  inner_join(power, by = c("subj_n", "rep_n")) %>% 
  mutate(power = round(power * 100, 0))
head(plot_diffs)
```

plot

```{r}
p_diffs <- plot_diffs %>%
  ggplot(aes(x = exp, y = mean_diff, ymin = Q2.5, ymax = Q97.5)) +
  geom_pointrange(fatten = 1/2, aes(colour=below_zero)) +
  geom_hline(yintercept = b0, colour = "red") +
  geom_hline(yintercept = 0.5, colour = "blue") + # this would add a line at b1 - the target effect size
  scale_colour_manual(values=c("darkgrey","black")) +
  geom_text(aes(x=50, y=-1,
                label = sprintf("%.f%s", power, "% power")), color = "darkgrey", size = 4) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "sim # (i.e., simulation index)",
       y = "difference score (standard units)") +
  scale_x_discrete(breaks = NULL) +
  facet_grid(fct_rev(factor(subj_n)) ~ rep_n) 
p_diffs

ggsave ("figures/diffs.jpeg",
        width = 6, height = 6)
```


ok, so my intuition is not quite right here. I'm clearly not doing something 
right with the way trial number is relating to precision. From what I can see, the
following things are the current situation:

1. increasing trials, makes the mean point estimate closer to the target. e.g., 
0.5. There is less variability.

2. Increasing sample size reduces the width of the 95% CI and thus increases power.

3. But increasing trial count is not making a difference to the width of the CI
and thus power. Even in a case where data included 80k datapoints in total
(N=20, rep_n = 100 plus the rest of the conditions and items), power was still 0.

This seems discrepant from the power contours paper. Or maybe not as discrepant as 
I initially thought. If I plug the within and between sigma values for the 
standardised data into the power contours app, I get N=63, K=12. If I compare that
to my data (granted this is just the raw data and 95% CI rather than a model),
we see that N=50, K=10 gives 97% power. So there is something different in the 
computation between my sims and power contours. The effect of trial count seems 
the same (e.g., low is fine and increasing it makes no difference). But the N is
discrepant. N=50 gives 97% power in my sims, but something closer to N=90 would
give 90% power in the power contours app.

Maybe I need to use a different dataset??? Original units? Or past data? Or super
simple data to take a closer look.

I wonder if trial count is being counted in the same way? In power contours, does
K=10 mean 10 per condition? Or per pid?
